Staged Abstract Interpreters

### 2018-10-18 paper/abstract.tex
revise abstract

It is well known that a staged interpreter is a compiler, which provides performance improvement
by eliminate the overhead of traversing the abstract syntax tree.

In this paper, we study staged \textit{abstract} interpreters.

We show staged abstract interpreters have practical applications rather than just theoretical merit.
The time consumed of a analysis can be decreased by staging (TODO: to what degree). We evaluate
the improvement of performance on benchmark programs.
Another application of staged abstract interpreter is to transform whole-program analysis
to modular analysis without losing precison. The generated code can be viewed as a 
partially analyzed result, which also can be composed and used latter with other modulars
in the program.

>>>>

It is well known that a staged interpreter is a compiler, which provides performance improvement
by specializing the interpreter to a given program.

In this paper, we study \textit{abstract} interpreters with multi-stage programming, i.e., the 
staged abstract interpreters. 
By staging an abstract interpreter respect to a program, we obtain a compiled and faster analysis.
By appying the idea to \textit{open} programs, we obtain a modular analysis that generates sound
partial analysis results which can be composed and reused later without losing precision, though 
the original abstract interpreter is a whole-program analysis algorithm.

We show several case studies using the idea of staged abstract interpreters, including 
\citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation of Shiver's 0-CFA, pushdown
control-flow analysis with context/path/flow-sensitivity and store-widening, and a numerical
analysis on a imperative language.

We also evaluate the improvement of performance on benchmark programs for a subset of Scheme.
The result shows ...
